Staged Abstract Interpreter

### 2018-01-05 paper.tex
related work

\citeauthor{Johnson:2013:OAA:2500365.2500604} in their work also adopt the 
idea closure generation for optimizing small-step abstracting abstract machine
\cite{Johnson:2013:OAA:2500365.2500604}.

>>>>

\citeauthor{Johnson:2013:OAA:2500365.2500604} in their work also adopt the 
idea closure generation for optimizing small-step abstracting abstract machine
\cite{Johnson:2013:OAA:2500365.2500604}. The source program is firstly compiled
to intermediate form called "abstract bytecode", which are actually higher-order functions, 
and then executed on a abstract abstract machine.

\citeauthor{damian1999partial}'s work on partial evaluation for program analysis \cite{damian1999partial}.

\citeauthor{amtoft1999partial}'s work on partial evaluation for constraint-based 
control flow analysis \cite{amtoft1999partial}.
